Do motif roles provide unique information about species risk of extinction?\\ \medskip Supplementary Information

### 2021-10-13 manuscript/supplement_motifs.tex
updated persistence vs SCg

            To test for effects of global network properties, we fit a linear regression relating consumer species' probabilities of persistence to network size, connectance, the level of disturbance to basal resources, and all interactions between them. 
            All predictors were centered and scaled before fitting the model. 
            As the three-way interaction was significant, we did not simplify the model.
            All models were fit using the R~\citep{R} base function `lm'.

            \begin{equation}
                \Psi_{ink} \approx \Sigma_{n} + \zeta_{n} + \pi_{k} + \Sigma_{n}:\zeta_{n} + \Sigma_{n}\pi_{k} + \zeta_{n}\pi_{k} + \Sigma_{n}\zeta_{n}\pi_{k},
                \label{SCeq}
            \end{equation}
            where all symbols are as in equation~\ref{propreq} and~\ref{partic_SC}.

@@

            \begin{equation}
                    \Psi_{ink} \approx \delta_{i} + \pi_{k} + \delta_{i}\pi_{k} +
                    S_{n}C_{n} ,
                    \label{degeq}
                \end{equation}

            \begin{equation}
                    \Psi_{ink} \approx \tau_{i} + \pi_{k} + \tau_{i}\pi_{k} +
                    S_{n}C_{n} ,
                    \label{TLeq}
                \end{equation}

@@

    % Updated with new random effect
    \begin{table}[h!]
        \centering
        \caption{Coefficients ($\beta$) and $p$-values ($p$) for models relating persistence to the proportion of a species' role made up by the focal motif, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction, as well as random effects to account for differences in persistence across levels of network size and connectance and connectance (Equation~\ref{propreq}). Predictors were centered and scaled before model fitting. We also provide the marginal $R^2_M$ (fixed effects only) and conditional $R^2_C$ (fixed and random effects) for each model.}
        \label{tab:proportion}                \footnotesize
        \begin{tabular}{c|c c | c c | c c | c c | c c |}
        & \multicolumn{2}{c|}{Intercept} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c|}{Disturbance} & \multicolumn{2}{c|}{Interaction} & \multicolumn{2}{c|}{$R^2$} \\
        Motif & $\beta$ & $p$ & $\beta$ & $p$ & $\beta$ & $p$ & $\beta$ & $p$ & $R^2_M$ & $R^2_C$ \\
        \hline
        3-sp Chain & 0.574 & \textless0.001 & -0.00492 & \textless0.001 & -0.139 & \textless0.001 & -0.00337 & \textless0.001 & 0.900 & 0.912 \\
        App. Com. & 0.574 & \textless0.001 & -0.00390 & \textless0.001 & -0.139 & \textless0.001 & 0.00410 & \textless0.001 & 0.900 & 0.911 \\
        Dir. Com. & 0.574 & \textless0.001 & 0.00607 & \textless0.001 & -0.139 & \textless0.001 & 0.000256 & \textless0.001 & 0.901 & 0.911 \\
        Omnivory & 0.575 & \textless0.001 & 0.00806 & \textless0.001 & -0.139 & \textless0.001 & -0.00198 & \textless0.001 & 0.894 & 0.912 \\
        \end{tabular}
    \end{table}        
\clearpage

@@

    \begin{table}[h!]
        \caption{Coeffcients ($\beta$) for regressions of consumers' probabilities of persistence against simple measures of species' role (STL or in-degree), level of disturbance to basal resources, and their interaction. Predictors were centered and scaled before model fitting. All $p$-values were \textless0.001. The level of disturbance is reflected by basal resources having a baseline probability of extinction ranging between $0.1 - 0.5$.}
        \label{tab:per_vs_TLdeg}
        \centering
        \begin{tabular}{l|c  c  c |}
            Simple role measure & Role & Disturbance & Interaction \\
            \hline
            STL & -0.0218 & -0.139 & 0.00508 \\
            in-degree & -0.00130 & -0.139 & -0.00908 \\
        \end{tabular}
    \end{table}

@@

    \begin{table}[hb!]
        \caption{Persistence of consumers within a network depends on network size (S) and connectance (C), the level of disturbance to basal resources (D), and interactions between them. Here we show the effect sizes ($\beta$) and $p$-values for the regression described above. All predictors were centered and scaled before fitting the model. The level of disturbance corresponds to basal resources having a probability of extinction ranging between $0.1 - 0.5$ (see \emph{Methods}).
        }
        \label{tab:per_vs_SC}
        \centering
        \begin{tabular}{c|c c |}
            Predictor & $\beta$ & $p$-value \\
            \hline
            Intercept & 0.572 & \textless0.001 \\
            Size & -5.15$\times10^{-4}$  & \textless0.001 \\
            Connectance & -0.0129 & \textless0.001 \\
            Disturbance & -0.139 & \textless0.001 \\
            S:C & -5.24$\times10^{-4}$ & \textless0.001 \\
            S:D & -3.48$\times10^{-3}$ & \textless0.001 \\
            C:D & -7.00$\times10^{-5}$ & 0.095 \\
            S:C:D: & -2.69$\times10^{-4}$ & \textless0.001 \\
        \end{tabular}
    \end{table}

>>>>

            To test for effects of global network properties, we fit a linear regression relating the mean of consumer species' probabilities of persistence in a network to network size, connectance, the level of disturbance to basal resources, and all interactions between them. 
            All predictors were centered and scaled before fitting the model. 
            As the three-way interaction was significant, we did not simplify the model.
            All models were fit using the R~\citep{R} base function `lm'.

            \begin{equation}
                \overline{\Psi_{nk}} \approx \Sigma_{n} + \zeta_{n} + \pi_k + \Sigma_{n}:\zeta_{n} + \Sigma_{n}\pi_k + \zeta_{n}\pi_k + \Sigma_{n}\zeta_{n}\pi_k,
                \label{SCeq}
            \end{equation}
            where all symbols are as in equation~\ref{propreq} and~\ref{partic_SC}.

@@

            \begin{equation}
                    \Psi_{ink} \approx \delta_{i} + \pi_{k} + \delta_{i}\pi_{k} +
                    S_{n}C_{n} + N_n,
                    \label{degeq}
                \end{equation}

            \begin{equation}
                    \Psi_{ink} \approx \tau_{i} + \pi_{k} + \tau_{i}\pi_{k} +
                    S_{n}C_{n} N_n,
                    \label{TLeq}
                \end{equation}

@@

    % Updated with new random effect
    \begin{table}[h!]
        \centering
        \caption{Coefficients ($\beta$) and $p$-values ($p$) for models relating persistence to the proportion of a species' role made up by the focal motif, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction, as well as random effects to account for differences in persistence across levels of network size, connectance, and network ID  (Equation~\ref{propreq}). Predictors were centered and scaled before model fitting. We also provide the marginal $R^2_M$ (fixed effects only) and conditional $R^2_C$ (fixed and random effects) for each model.}
        \label{tab:proportion}                \footnotesize
        \begin{tabular}{c|c c | c c | c c | c c | c c |}
        & \multicolumn{2}{c|}{Intercept} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c|}{Disturbance} & \multicolumn{2}{c|}{Interaction} & \multicolumn{2}{c|}{$R^2$} \\
        Motif & $\beta$ & $p$ & $\beta$ & $p$ & $\beta$ & $p$ & $\beta$ & $p$ & $R^2_M$ & $R^2_C$ \\
        \hline
        3-sp Chain & 0.574 & \textless0.001 & -0.00492 & \textless0.001 & -0.139 & \textless0.001 & -0.00337 & \textless0.001 & 0.900 & 0.912 \\
        App. Com. & 0.574 & \textless0.001 & -0.00390 & \textless0.001 & -0.139 & \textless0.001 & 0.00410 & \textless0.001 & 0.900 & 0.911 \\
        Dir. Com. & 0.574 & \textless0.001 & 0.00607 & \textless0.001 & -0.139 & \textless0.001 & 0.000256 & \textless0.001 & 0.901 & 0.911 \\
        Omnivory & 0.575 & \textless0.001 & 0.00806 & \textless0.001 & -0.139 & \textless0.001 & -0.00198 & \textless0.001 & 0.894 & 0.912 \\
        \end{tabular}
    \end{table}        
\clearpage

@@

    % Updated with network-level random effect
    \begin{table}[h!]
        \caption{Coeffcients ($\beta$) for linear mixed-effect models of consumers' probabilities of persistence against simple measures of species' role (STL or in-degree), level of disturbance to basal resources, and their interaction, as well as a random effect of network ID. Predictors were centered and scaled before model fitting. All $p$-values were \textless0.001. The level of disturbance is reflected by basal resources having a baseline probability of extinction ranging between $0.1 - 0.5$.}
        \label{tab:per_vs_TLdeg}
        \centering
        \begin{tabular}{l|c  c  c |}
            Simple role measure & Role & Disturbance & Interaction \\
            \hline
            STL & -0.0210 & -0.139 & 0.00508 \\
            in-degree & -0.00188 & -0.139 & -0.00908 \\
        \end{tabular}
    \end{table}

@@

    % Updated to use mean rather than all species.
    \begin{table}[hb!]
        \caption{Mean persistence of consumers within a network depends on network size (S) and connectance (C), the level of disturbance to basal resources (D), and interactions between them. Here we show the effect sizes ($\beta$) and $p$-values for the regression described above. All predictors were centered and scaled before fitting the model. The level of disturbance corresponds to basal resources having a probability of extinction ranging between $0.1 - 0.5$ (see \emph{Methods}).
        }
        \label{tab:per_vs_SC}
        \centering
        \begin{tabular}{c|c c |}
            Predictor & $\beta$ & $p$-value \\
            \hline
            Intercept & 0.574 & \textless0.001 \\
            Size & -4.82$\times10^{-4}$  & 0.011 \\
            Connectance & -0.0137 & \textless0.001 \\
            Disturbance & -0.139 & \textless0.001 \\
            S:C & -9.77$\times10^{-4}$ & \textless0.001 \\
            S:D & -3.46$\times10^{-3}$ & \textless0.001 \\
            C:D & -2.25$\times10^{-4}$ & 0.233 \\
            S:C:D: & -3.97$\times10^{-4}$ & 0.036 \\
        \end{tabular}
    \end{table}
